1000 Graphs

### 2021-06-27 graphs_newt_snakes/fig_1000.Rmd
added a graph showing the difference between the means. Next step is to figure out what sims are going to the extreams.

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max_3 = 0

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
  #print(max(file$Snake_max_Pheno, na.rm = TRUE))
  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno){
    newt_max_pheno = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }

  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno){
    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)
  if (newt_max_pheno > snake_max_pheno){
    true_max_3 = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max_3 = snake_max_pheno }
```
some of these values are in quotes, why?

@@

Some other things that might be goo to look at:
The average of the phenotypes
The difference between the average phenotypes

```{r pressure, echo=FALSE}
ggplot()+
  geom_line(current_file, aes(gen, snake), color="blue")+
  geom_line(current_file, aes(gen, snake), color="red")+
  geom_point(size=3, color = "darkgreen")+
  ggtitle("How the Phenotypes Change Through the Generations") + 
  xlab("Generation") + 
  ylab("Phenotype Level") +
  theme_bw()
```

>>>>

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max_3 = 0
max_difference = 0
min_difference = 0

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA

  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
  #print(max(file$Snake_max_Pheno, na.rm = TRUE))
  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno){
    newt_max_pheno = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }

  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno){
    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }

 if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference){
    min_difference = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference){
    max_difference = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  print(newt_max_pheno)
  print(snake_max_pheno)
  print(min_difference)
  print(max_difference)
  if (newt_max_pheno > snake_max_pheno){
    true_max_3 = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max_3 = snake_max_pheno }
```
some of these values are in quotes, why?

@@

Some other things that might be goo to look at:

The difference between the average phenotypes

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  scale_y_log10(limits=c(0.001, max_difference))+
  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
  theme_bw()

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
  file$mean_dif[file$mean_dif == 0] <- 0.01
  file$pos <- TRUE
  file$pos[file$mean_dif < 0] <- FALSE

 p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
  #Sys.sleep(2) na.rm=TRUE
 # color = "mediumseagreen"
